A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-01-27 src/tex/ms.tex
Updates from Overleaf

\begin{figure*}
    \centering
    \includegrac
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \includegraphics{src/tex/figures/ofe_df_yields.pdf}
    \caption{Stellar [O/Fe] distributions produced by multi-zone models (a, b) and as observed by APOGEE (c). Stars are binned by Galactocentric radius, represented by the color scale, and absolute midplane distance $|z|$, represented by the different rows. Each distribution is normalized so that the area under the curve is 1, and the vertical scale is consistent across each row. {\bf (a)} Multi-zone model output assuming the {\tt yZ1} yield set. {\bf (b)} Model output assuming the {\tt yZ2} yield set. {\bf (c)} The distributions from APOGEE DR17 for reference. {\bf Key takeaway:} }
    \label{fig:ofe-df-yields}
\end{figure*}
